---
title: "mod01_git"
author: "CJ Tinant"
date: "`r Sys.Date()`"
output: html_document
---

## Overview
This Rmd works through the version control module of the R4WRDS intermediate course: <https://r4wrds.netlify.app/intermediate/m_version_control>

**Learning objectives**

-   Understand and use basic git commands for version control

-   Develop a mindset and approach to set up and manage a version controlled project

-   Identify best practices for using git collaboratively

This lesson assumes you have:

-   Set up a Github Account

-   Installed git on your computer locally

```{r setup, include=FALSE}

# setting up git
knitr::opts_chunk$set(echo = TRUE)
library(usethis)

# download data
library(fs)
library(dataRetrieval)    # retrieval functions for usgs and epa hydrology 
                          # and water quality data
library(readr)            # read rectangular data 
library(glue)             # makes it easy to interpolate data into strings

# clean and visualize data
suppressPackageStartupMessages(
  library(tidyverse
          )
  )    # ignore ‘simple’ diagnostic messages at startup -- load tidyverse

suppressPackageStartupMessages(
  library(
    lubridate)
  )    # ignore ‘simple’ diagnostic messages at startup 
# lubridate makes dealing with dates a little easier


```

## Installing Git and configuring GitHub
We highly recommend Jenny Bryan & Jim Hester’s [happygitwithr](https://happygitwithr.com) website because it covers everything (and more) that you may encounter when using `git` with R. In particular, please take a moment to check/update your `git` installation and configure Github. The following links will help with this:

-   [**Install Git**](https://happygitwithr.com/install-git.html)

-   [**Introduce yourself to Git**](https://happygitwithr.com/hello-git.html)

## Git workflow process
The general process to follow is:

-   **work:** Do some work, add some files, scripts, etc. 

-   **add:** To version control these changes, we need to stage or add that work so it can be versioned by git. We do this with git add <my_file> or check the Staged buttons in the RStudio git panel.

-   **commit:** Add a commit message that is succinct but descriptive (i.e., added water data files). These are the messages you’ll be able to go back to if you want to travel back in time and see a different version of something…so be kind to your future self and add something helpful.

-   **push:** Finally, when we’re ready to send locally commited changes up the cloud, we push this up to the Github remote cloud repository!

### Try it yourself

Take the following function and: 

1. Make a new folder in your project called code, save as a script called 01_download_data.R 

2. stage it (either through the Git tab, or via git add), 

3. commit (add a message!), 

4. push to the jo_download_data branch

```{r download-data-function}

# make a function to download data, defaults to current date for end

# function: dates as "YYYY-MM-DD"
get_daily_flow <- function(gage_no){

  #  create folder to save data
  #  fs::dir_create("data_raw")

# set parameters to download data
siteNo <- gage_no # The USGS gage number
pCode <- "00060" # 00060 is discharge parameter code

  # get NWIS daily data: CURRENT YEAR
  dat <- readNWISdv(siteNumbers = siteNo,
                    parameterCd = pCode)
  # add water year
  dat <- addWaterYear(dat)
  # rename the columns
  dat <- renameNWISColumns(dat)

  # save out
  write_csv(dat,
            file =
              glue("data_raw/nfa_updated_{Sys.Date()}.csv"))
}

# RUN with:
#siteNo <- "11427000"   # NF American River
# get_daily_flow(siteNo)

```


```{r get-downloaded-data}

# list csv files in dir
files <- fs::dir_ls("data_raw", glob = "*gz")

# get file info to identify most recent
files_info <- fs::dir_info("data_raw",
                           regexp = "nfa_updated")

# get most recent file only if multiple exists/**9*
(file_recent <- files_info %>%
    select(path, modification_time) %>%
    arrange(modification_time) %>%
    slice_max(order_by = modification_time))

# remove any other files
files_info %>% filter(path!=file_recent$path) %>%
  pull(path) %>%
  fs::file_delete()

```



